Model

### 2019-09-04 stats/model.Rmd
update model

@@

@@

plot_global_params
```
```{r}
plot_global_sigma <- ggplot(global_sigma, aes(x = value, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  xlab("Sigma")+
  facet_grid(~parameter, scales = 'free')+
  theme_few()

@@

to do:
- bookkeeping: index correct participant/item variables at relevant part of code
- inference: try HMC, variational

subj | item | response
1    |  A  |   1
1    |  B  |   1
2    |  A  |   1
2    |  B  |   0

```{js}

var sampleItemParameters = function() { 
  return {
      intercept: gaussianDrift({
        mu: globalLineParameters.intercept, 
        sigma: itemVariability.intercept, 
        width: 0.5
      }),
      slope: Math.pow(gaussianDrift({
        mu: globalLineParameters.slope, 
        sigma: itemVariability.slope, 
        width: 0.5
      }), 2)
    }   
}

// want something that favors smaller values
var subject_sigma = uniform(0, 1)

var sampleLinguisticCompetence = function(age){
  return gaussianDrift({ mu: age, sigma: subject_sigma, width: 0.5 })
}

// [ carrot, duck, bread, ...]  (slope and intercept)
var all_item_parameters = repeat(n_items, sampleItemParameters)
// [s1, s2, s3, ...] (intercept)
var all_subject_parameters = map(sampleLinguisticCompetence, subjects)

var sem_knowledge = logistic(item.intercept +  item.slope * linguistic_competence)
```

@@

      // question: should we use age here instead of the random intercept? or a different random intercept?
      var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * age

@@

        var modelPredictions = pragmaticListener({label: "novel_word"}, prior, speakerOptimality, sem_knowledge)
        query.add(["prediction", item, row.age], [row.alignment, Math.exp(modelPredictions.score(1))])

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data, comb_data = comb_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 1,
  cores = 1,
  inference_opts = list(method = "incrementalMH",
                        samples = 1,
                        burn = 1,
                        verbose = T,
                        lag = 1,
                        verboseLag = 10)
)

# saveRDS(sem_know_model, "../saves/sem_know_model_wide_sig_pos_slope_ind.rds")

@@

>>>>

# Summarizing parameters

@@

model_pred<- sem_know_model %>%
  separate(Parameter, into = c("parameter", "item","age"), sep = ",")%>%
  filter(parameter == "prediction")%>%
  separate(value, into = c("alignment", "me_effect"),sep = ", ")%>%
  mutate(age = as.numeric(age),
         me_effect =str_remove(me_effect,"[)]"),
         me_effect =str_remove(me_effect,'"'),
         me_effect =as.numeric(str_remove(me_effect,'"')),
         alignment = str_remove(alignment,'c[(]'),
         alignment =str_remove(alignment,'"'),
         alignment =str_remove(alignment,'"'))

@@

plot_global_params
```

```{r}
plot_global_sigma <- ggplot(global_sigma, aes(x = value, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  xlab("Sigma")+
  facet_grid(~parameter, scales = 'free')+
  theme_few()

@@

@@

      // question: should we use age here instead of the random intercept? or a different random intercept?

  var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * subj_age

@@

        var modelPredictions = pragmaticListener({label: "novel_word"}, prior, speakerOptimality, sem_knowledge)

display(row.alignment)

        query.add(["prediction", item, row.age], [row.alignment, Math.exp(modelPredictions.score(1))])

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data, comb_data = comb_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 1,
  cores = 1,
  inference_opts = list(method = "incrementalMH",
                        samples = 10,
                        burn = 1,
                        verbose = T,
                        lag = 1,
                        verboseLag = 1000)
)

# run variants
# start with variant 3
# 3 cores, 3 chains 
# see how long it takes and then run over night

# saveRDS(sem_know_model, "../saves/sem_know_model_save pred.rds")

@@

#### plotting predictions

```{r}
comb_model_pred_agg <- model_pred%>%
  group_by(alignment,item,age)%>%
  summarise(mean = estimate_mode(me_effect),
            uci = hdi_upper(me_effect),
            lci = hdi_lower(me_effect))%>%
  left_join(aoa_ratings) %>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa),
         age = age + min(me_data$age_num))

ggplot(comb_model_pred_agg, aes(x=age,y = mean, col = item))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(size = 1)+
  ggtitle("Combination Model Predictions")+
  labs(x="Age",y="Proportion correct")+
  facet_grid(~alignment)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d()
